Enabling conditions for effective community-based marine reserves in small-scale fisheries

### 2018-03-22 docs/paper/Villasenor-Derbez.Rmd
fixed mistakes due to reorganization of repo

# Load indicator functions
source(file = here::here("scripts", "abundance.R")) #Calculate abundance per transect
source(file = here::here("scripts", "richness.R")) # Calculate richness per transect
source(file = here::here("scripts", "shannon.R")) #Calculate shannon's index per transect
source(file = here::here("scripts", "biomass.R")) # Calculate fish biomass per transect
source(file = here::here("scripts", "trophic.R")) # Calculate mean trophic level per transect

@@

# Load high-res mexican coastline
coastline_mx <- readRDS(here::here("data", "spatial", "coastline_mx.rds"))

@@

# Load ZRP shapefile
zrp <- st_read(dsn = here::here("data", "spatial"), layer = "ZRP", quiet = T) %>% 
  filter(Name %in% c("El Cabezo", "El Faro")) %>% 
  st_transform(crs = "+proj=longlat +datum=NAD27")

# Load Community reserve shapefile
rescom <- st_read(dsn = here::here("data", "spatial"), layer = "Res_Com", quiet = T) %>% 
  filter(Nombre == "La_Plana") %>% 
  st_transform(crs = "+proj=longlat +datum=NAD27")

@@

conapesca <- read.csv(x = conapesca, file = here::here("data", "conapesca.csv"))

@@

group_by(fish, comunidad, rc, zona, sitio, transecto, ano) %>%
  count() %>% 
  ungroup() %>% 
  group_by(comunidad, rc, zona) %>% 
  summarize(ano = min(ano), n = n()) %>% 
  ungroup() %>% 
  spread(zona, n) %>% 
  mutate(implementation = c(2006, 2012, 2013, 2013)) %>% 
  select(comunidad, implementation, ano, rc, control = Control, reserve = Reserva) %>% 
  left_join(inv_summary, by = c("comunidad", "rc")) %>% 
  knitr::kable(format = "latex",
               caption = "\\label{table:com_sum} Summary of commuity--based marine reserves by community. Imp = Year of implementation, Start = Year of first sampling, number of fish transects in control (Cf) and reserve (Rf) sites, and number of invertebrate transects in Control (Ci) and Reserve (Ri) sites.",
               col.names = c("Community", "Reserve - Control", "Imp", "Start", "Cf", "Rf", "Ci", "Ri"))
```

@@

cowplot::plot_grid(plotlist = list(L_plot, F_B, I_N, F_N),
                   labels = "AUTO",
                   ncol = 2)

```{r, fig.height = 3, fig.width = 6, fig.cap = "\\label{fig:res_com}Summarized effects of the marne reserves by direction (positive - negative) and significance."}
observe <- function(model){      tidy_terms <- model %>% 
        robust_se() %>%
        filter(grepl(":ZonaReserva", term)) %$%
        str_split(term, pattern = ":", simplify = T) %>% 
        as.tibble() %>% 
        set_colnames(c("Ano", "Zona")) %>% 
        select(-Zona) %>% 
        mutate(Ano = as.numeric(gsub(Ano, pattern = "Ano", replacement = "")))

      p_i <- robust_se(model) %>%
        filter(grepl(":ZonaReserva", term)) %>%
        cbind(tidy_terms) %>%
        mutate(ptest = ((p.value < 0.05)*-1)+0.05)
       return(p_i)}

@@

rbind(IN, ME, PH) %>% 
  mutate(direction = case_when(estimate < 0 ~ "Negative",
                               estimate > 0 ~ "Positive"),
         Significance = case_when(p.value < 0.05 ~ "p < 0.05",
                            p.value >= 0.05 ~ "p > 0.05")) %>%
  group_by(Com, direction, Significance, n_ind) %>% 
  summarize(A = n()) %>% 
  ungroup() %>% 
  mutate(A = A/n_ind,
         A = ifelse(direction == "Negative", -A, A),
         Significance = fct_relevel(Significance, "p > 0.05")) %>% 
  ggplot(aes(x = Com, y = A, fill = Significance)) +
  geom_col(color = "black", alpha = 0.8, width = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  coord_flip() +
  labs(x = "Community", y = "Percentage of total coefficients") +
  scale_y_continuous(breaks = seq(-0.65, 0.9, by = 0.25), limits = c(-0.65, 0.9),
                     labels = scales::percent) +
  theme(legend.text = element_text(size = 8),
        legend.title = element_text(size = 8))
```

>>>>

# Load indicator functions
source(file = here::here("scripts", "abundance.R")) #Calculate abundance per transect
source(file = here::here("scripts", "biomass.R")) # Calculate fish biomass per transect
source(file = here::here("scripts", "trophic.R")) # Calculate mean trophic level per transect

@@

# Load high-res mexican coastline
coastline_mx <- readRDS(here::here("raw_data", "spatial", "coastline_mx.rds"))

@@

# Load ZRP shapefile
zrp <- st_read(dsn = here::here("raw_data", "spatial"), layer = "ZRP", quiet = T) %>% 
  filter(Name %in% c("El Cabezo", "El Faro")) %>% 
  st_transform(crs = "+proj=longlat +datum=NAD27")

# Load Community reserve shapefile
rescom <- st_read(dsn = here::here("raw_data", "spatial"), layer = "Res_Com", quiet = T) %>% 
  filter(Nombre == "La_Plana") %>% 
  st_transform(crs = "+proj=longlat +datum=NAD27")

@@

conapesca <- read.csv(file = here::here("data", "conapesca.csv"))

@@

group_by(fish, comunidad, rc, zona, sitio, transecto, ano) %>%
  count() %>% 
  ungroup() %>% 
  group_by(comunidad, rc, zona) %>% 
  summarize(ano = min(ano), n = n()) %>% 
  ungroup() %>% 
  spread(zona, n) %>% 
  mutate(implementation = c(2006, 2012, 2013, 2013)) %>% 
  select(comunidad, rc, implementation, ano, control = Control, reserve = Reserva) %>% 
  left_join(inv_summary, by = c("comunidad", "rc")) %>% 
  knitr::kable(format = "latex",
               caption = "\\label{table:com_sum} Summary of commuity--based marine reserves by community. Imp = Year of implementation, Start = Year of first sampling, number of fish transects in control (Cf) and reserve (Rf) sites, and number of invertebrate transects in Control (Ci) and Reserve (Ri) sites.",
               col.names = c("Community", "Reserve - Control", "Imp", "Start", "Cf", "Rf", "Ci", "Ri"))
```

@@

cowplot::plot_grid(plotlist = list(L_plot, F_B, I_N, F_N),
                   labels = "AUTO",
                   ncol = 2)
```

```{r, fig.height = 3, fig.width = 6, fig.cap = "\\label{fig:res_com}Summarized effects of the marne reserves by direction (positive - negative) and significance."}
observe <- function(model){
  tidy_terms <- model %>% 
        robust_se() %>%
        filter(grepl(":zonaReserva", term)) %$%
        str_split(term, pattern = ":", simplify = T) %>% 
        as.tibble() %>% 
        set_colnames(c("Ano", "Zona")) %>% 
        select(-Zona) %>% 
        mutate(Ano = as.numeric(gsub(Ano, pattern = "year", replacement = "")))

      p_i <- robust_se(model) %>%
        filter(grepl(":zonaReserva", term)) %>%
        cbind(tidy_terms) %>%
        mutate(ptest = ((p.value < 0.05)*-1)+0.05)

       return(p_i)
      }

@@

rbind(IN, ME, PH) %>% 
  mutate(direction = case_when(estimate < 0 ~ "Negative",
                               estimate > 0 ~ "Positive"),
         Significance = case_when(p.value < 0.05 ~ "p < 0.05",
                            p.value >= 0.05 ~ "p > 0.05")) %>%
  group_by(Com, direction, Significance, n_ind) %>% 
  summarize(A = n()) %>% 
  ungroup() %>% 
  mutate(A = A/n_ind,
         A = ifelse(direction == "Negative", -A, A),
         Significance = fct_relevel(Significance, "p > 0.05")) %>% 
  ggplot(aes(x = Com, y = A, fill = Significance)) +
  geom_col(color = "black", alpha = 0.8, width = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  coord_flip() +
  labs(x = "Community", y = "Percentage of total coefficients") +
  scale_y_continuous(breaks = seq(-0.5, 1, by = 0.25), limits = c(-0.5, 1),
                     labels = scales::percent) +
  theme(legend.text = element_text(size = 8),
        legend.title = element_text(size = 8))
```
